### 2016-07-08 overlay_fs.tex
Test
Undo Test and change move to copy
minor change
fixed mistake
Trying to write memory card

Originally, the home folder is located in the root filesystem. Although,
we have to move its content to the new home partition and store it properly

@@

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card.
The testbed administrator needs to insert each memory card in its \ac{PC}
and follow the procedure in this section. A given card will be available as
\texttt{/dev/mmcblk*} or \texttt{/dev/sd*} with X a given

For internal memory card readers,
it will probably be named /dev/mmcblkX where X is a given integer number
and if the memory card reader is connected through \ac{USB}, then it is likely called /dev/sdX. It is very important Make absolutely sure to write to the correct device as everything will be overwritten!
Inserting/Ejecting the memory card a couple of times and using the commands
below may help deducing the correct device:
%The commands below may help deduce which device is the correct:
%Below is a few commands that may help you to deduce which device is correct:

\begin{lstlisting}[]
# lsblk
# df -h
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

For us, the device was \texttt{/dev/mmcblk0}. Write the image to a memory card:
\begin{lstlisting}[]
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M && sync
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

The memory card can now be started in a \ac{Raspi}.

>>>>

Originally, the home folder is located in the root filesystem. Although,
we have to move its content to the new home partition and store it properly.
We do that as follows:

@@

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card.
The testbed administrator needs to insert each memory card in its \ac{PC}
and follow the procedure in this section. A given card will be available as
\texttt{/dev/mmcblkX} for memory card readers or \texttt{/dev/sdX} USB-through
readers , where \texttt{X} a natural number. It is \textit{very important}
to write to the correct device as everything will be overwritten. To avoid
removing information from the wrong device, a testbed administrator can
insert / eject a memory card a couple of times and using the
\texttt{sudo lsblk} and \texttt commands to deduce the correct device.

For our case, the device was \texttt{/dev/mmcblk0}. Once identified, to write
the image to a memory card, the following command is used:

\begin{lstlisting}[]
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M && sync
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

After this is made, the memory card can now be started in a \ac{Raspi}.
